---
title: "Categorical Embeddings: New Ways to Simplify Complex Data"
subtitle: "rstudio::global(2020)"
author: "Alan Feder <br /> <br />Principal Data Scientist <br /> Invesco"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---
class: hide-count

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{css echo=FALSE}
.hide-count .remark-slide-number {
  display: none;
}
```

# Libraries

```{r libraries, message=FALSE}
library(tidyverse)
library(tidymodels)
library(reticulate)
use_condaenv("r-keras2")
library(keras)
library(embed) #<<

set.seed(1818)
```

---
class: hide-count

# Data

```r
data(sales, package = "DMwR2")
glimpse(sales)
```

```{r import-data, include=FALSE}
data(sales, package = "DMwR2")
sales
```

```{r show-data, echo=FALSE}
glimpse(sales)
```

```{r n-distinct-prods}
n_distinct(sales$Prod)
```

```{r split-train}
sales_split <- initial_split(sales, strata = Insp)
sales_train <- training(sales_split)
```

---
class: hide-count

# Recipe

```{r create-recipe}
sales_recipe <- recipe(sales_train) %>%
  update_role(Quant, Val, Prod, new_role = "predictor") %>%
  update_role(Insp, new_role = "outcome") %>%
  step_rm(ID) %>%
  step_naomit(Quant, Val) %>%
  step_filter(Insp != "unkn") %>%
  step_center(Quant, Val) %>%
  step_scale(Quant, Val) %>%
  step_embed(Prod, num_terms = 4, hidden_units = 16, outcome = vars(Insp), #<<
             options = embed_control(loss = "binary_crossentropy", epochs = 10)) #<<
```

```{r create-embeds, message=FALSE, warning=FALSE}
trained_sales_recipe <- prep(sales_recipe)
```

---
class: hide-count

# Embeddings

```r
trained_sales_recipe$steps[[6]]$mapping$Prod %>%
  relocate(..level) %>%
  head(5)
```

```{r show-prod, echo=FALSE}
trained_sales_recipe$steps[[6]]$mapping$Prod %>%
  relocate(..level) %>%
  head(5) %>%
  knitr::kable(format = "html")
```

---
class: hide-count

# Thank you!

* slides, code, and more details: https://github.com/rstudio/rstudio-conf/tree/master/2021/alanfeder
* contact: AlanFeder@gmail.com  
* Twitter: @AlanFeder

# Acknowledgements

* I first learned about categorical embeddings from **fastai: Practical Deep Learning for Coders**, by Jeremy Howard
* Data and analysis steps taken from **TensorFlow training** at **RStudio::conf(2019)**, by Sigrid Keydana, Kevin Kuo, and Rick Scavetta
