---
title: "Resolving merge conflicts"
author: "Dr. Çetinkaya-Rundel"
date: "2018-01-29"
output:
  xaringan::moon_reader:
    css: "slides.css"
    logo: img/sta199-logo-hex.png
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(magick)
library(knitr)
library(emo)
library(mosaicData)
library(openintro)
library(DT)
```

```{r setup, include=FALSE}
# R options
options(
  htmltools.dir.version = FALSE, # for blogdown
  show.signif.stars = FALSE,     # for regression output
  warm = 1
  )
# Set dpi and height for images
opts_chunk$set(fig.height = 2.65, dpi = 300) 
# ggplot2 color palette with gray
color_palette <- list(gray = "#999999", 
                      salmon = "#E69F00", 
                      lightblue = "#56B4E9", 
                      green = "#009E73", 
                      yellow = "#F0E442", 
                      darkblue = "#0072B2", 
                      red = "#D55E00", 
                      purple = "#CC79A7")
# For nonsese...
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
# For magick
dev.off <- function(){
  invisible(grDevices::dev.off())
}
```


## Announcements

Please sit with your teams in class and lab

---

class: center, middle

# Merge conflicts

---

## Merge conflicts

- When two collaborators make changes to a file and push the file to their repo, git merges these two files.

- If these two files have conflicting content on the same line, git will produce a **merge conflict**.

---

## Getting started

- Clone your assignment repo in RStudio Cloud (`hw-01-dataviz-teamname`), and open the .Rmd file.

- Assign the numbers 1, 2, 3 (and 4, if you have 4 members) to each of the team members.

---

## Let's cause a merge conflict

Take turns in completing the exercise, only one member at a time. For now, only commit and push the Rmd file:

- Member 1 - Change the team name to your actual team name, knit, commit, push.

- Member 2 - Change the team name to some other word, knit, commit, push. You should get an error. Pull. Take a look at the document with the merge conflict. Clear the merge conflict by choosing the correct/preferred change. Commit, and push.

- Member 3 - Add a name to the first code chunk, knit, commit, push. You should get an error. Pull. No merge conflicts should occur. Now push.

- Member 4 - Add a different name to the first code chunk, knit, commit, push. You should get an error. Pull. Take a look at the document with the merge conflict. Clear the merge conflict by choosing the correct/preferred change. Commit, and push.

- All members - Pull, and observe the changes in your document.

---

## Tips for collaborating via git/GitHub

- Always pull first before you start working.

- Commit, and push, often to minimize merge conflicts and/or to make merge conflicts easier to resolve.

- If you find yourself in a situation that is difficult to resolve, ask questions asap, don't let it linger and get bigger.
