---
title: "ggedit RStudio::conf 2017 Presentation"
author: "Jonathan Sidi"
date: "January 13, 2017"
output: pdf_document
classoption: landscape
---

Metrum Research Group [\@MetrumRG](https://twitter.com/MetrumRG)

Jonathan Sidi [\@yoniceedee](https://twitter.com/yoniceedee)

[ggedit github dev repo](https://github.com/metrumresearchgroup/ggedit)

[Metrum open source tools](http://metrumrg.com/opensourcetools.html)

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=7, fig.path='RstudioConf/Figs/', warning=FALSE, message=FALSE)
```

```{r}
#devtools::install_github("metrumresearchgroup/ggedit",subdir="ggedit")
rm(list=ls())
library(ggedit)
#?ggedit

p0=list(
  Scatter=iris%>%ggplot(aes(x =Sepal.Length,y=Sepal.Width))+
    geom_point(aes(colour=Species),size=6),
  
  ScatterFacet=iris%>%ggplot(aes(x =Sepal.Length,y=Sepal.Width))+
    geom_point(aes(colour=Species),size=6)+
      geom_line(linetype=2)+
    facet_wrap(~Species,scales='free')+
    labs(title='Some Title')
  )

#a=ggedit(p.in = p0,verbose = T) #run ggedit
dat_url <- paste0("https://raw.githubusercontent.com/metrumresearchgroup/ggedit/master/RstudioExampleObj.rda")
load(url(dat_url)) #pre-run example

ldply(a,names)

plot(a)

comparePlots=c(p0,a$UpdatedPlots)
names(comparePlots)[c(3:4)]=paste0(names(comparePlots)[c(3:4)],"Updated")
```

#Initial Comparison Plot
```{r}
plot(as.ggedit(comparePlots))
```

#Apply updated theme of first plot to second plot
```{r}
comparePlots$ScatterFacetNewTheme=p0$ScatterFacet+a$UpdatedThemes$Scatter

plot(as.ggedit(comparePlots[c("ScatterFacet","ScatterFacetNewTheme")]),
      plot.layout = list(list(rows=1,cols=1),list(rows=2,cols=1))
     )
```
#Using Remove and Replace Function
##Overlay two layers of same geom
```{r}
(comparePlots$ScatterMistake=p0$Scatter+a$UpdatedLayers$ScatterFacet[[1]])
```

##Remove
```{r}
(comparePlots$ScatterNoLayer=p0$Scatter%>%
  rgg(oldGeom = 'point'))
```

##Replace Geom_Point layer on Scatter Plot
```{r}
(comparePlots$ScatterNewLayer=p0$Scatter%>%
  rgg(oldGeom = 'point',
      oldGeomIdx = 1,
      newLayer = a$UpdatedLayers$ScatterFacet[[1]]))
```

##Remove and Replace Geom_Point layer and add the new theme
```{r}
(comparePlots$ScatterNewLayerTheme=p0$Scatter%>%
  rgg(oldGeom = 'point',
      newLayer = a$UpdatedLayers$ScatterFacet[[1]])+
  a$UpdatedThemes$Scatter)
```

#Cloning Layers
##A geom_point layer
```{r}
(l=p0$Scatter$layers[[1]])
```

##Clone the layer
```{r}
(l1=cloneLayer(l))
```

###Test that all is equal
```{r}
all.equal(l,l1)
```

##Verbose copy of layer
```{r}
(l1.txt=cloneLayer(l,verbose = T))
```

###Parse the text
```{r}
(l2=eval(parse(text=l1.txt)))
```

###Test that all is equal
```{r}
all.equal(l,l2)
```

#Back to our example
```{r}
  #Original geom_point layer
  parse(text=cloneLayer(p0$ScatterFacet$layers[[1]],verbose = T))
  #new Layer
  parse(text=a$UpdatedLayerCalls$ScatterFacet[[1]])
```

#Visualize Themes
```{r}
pTheme=list()
(pTheme$Base=plot(a$UpdatedThemes$Scatter))
```

##Visualize Part of Themes
```{r}
(pTheme$Select=plot(a$UpdatedThemes$Scatter,themePart = c('plot','legend'),fnt = 18))
```

##Visually Compare Theme
```{r}
(pTheme$Compare=plot(obj=a$UpdatedThemes$Scatter,obj2 = ggplot2:::theme_get()))
```