---
title: "Prep + brainstorming for Denny's / La Quinta lab"
output: html_notebook
---

Load packages:

```{r load-packages}
library(tidyverse)
library(rvest)
```

# Pre-lab

Load data:

```{r load-data}
dn <- read_csv("data-raw/dennys-raw.csv")
lq <- read_csv("data-raw/laquinta-raw.csv")
```

## Same-ify Denny's and La Quinta data

### La Quinta data cleanup:

- Fix Canada ~~zip~~ post codes:

```{r fix-ca-zip}
lq$Address[639] <- "63 King Street East,\nOshawa, ON L1H1B4"
lq$Address[867] <- "8640 Alexandra Rd,\nRichmond, BC V6X1C4"
```

- Fix nonstandard patterns:

```{r fix-pattern}
lq$Address[188] <- "3201 Macon Rd Suite A,\nColumbus, GA 31906-1717"
lq$Address[522] <- "Carrera 38 # 26-13 Avenida las Palmas con Loma de San Julian El Poblado,\nMedellin Colombia, ANT 050016"
lq$Address[656] <- "101 South Frontage Road I-20 West,\nPecos, TX 79772"
lq$Address[762] <- "Av. Benito Juarez 1230 B (Carretera 57) Col. Valle Dorado Zona Hotelera,\nSan Luis Potosi, SL 78399"
lq$Address[705] <- "2180 Hilltop Dr,\nRedding, CA 96002-0512"
```

- Fix variable names and order and split addresses into columns:

```{r fix-vars-split-address}
lq <- lq %>%
  select(-c(Name, Phone, Fax)) %>%
  rename(
    address = Address,
    longitude = Longitude,
    latitude = Latitude
  ) %>%
  separate(address, c("address", "city", "state_zip"), sep = ",") %>%
  mutate(state_zip = str_trim(state_zip)) %>%
  separate(state_zip, c("state", "zip"), sep = " ") %>%
  mutate(zip = str_replace(zip, "-(.*)", ""))
```

### Denny's data cleanup 

Variable names and order:

```{r fix-vars-order}
dn <- dn %>%
  rename(
    address = Address,
    city = City,
    state = State,
    zip = Zip,
    longitude = Longitude,
    latitude = Latitude
  ) %>%
  select(address, city, state, zip, longitude, latitude)
```

## Prep states data

Get state abbreviations from R:

```{r state-abb}
state_abb <- tibble(
  name = state.name, 
  abbreviation = state.abb
) %>%
  add_row(name = "District of Columbia", abbreviation = "DC")
```

Get state areas from Wikipedia:

```{r state-wiki-scrape}
wiki_page <- read_html("https://en.wikipedia.org/wiki/List_of_U.S._states_and_territories_by_area")
```

```{r collect-states-info}
state_names <- wiki_page %>%
  html_nodes("td:nth-child(1) , .headerSort:nth-child(1)") %>%
  html_text() %>%
  tibble(name = .) %>%
  mutate(name = str_trim(name)) %>%
  slice(1:51)
                                                                                       state_areas <- wiki_page %>%
  html_nodes("h2+ .jquery-tablesorter .headerSort:nth-child(3) , td~ td+ td:nth-child(3)") %>%
  html_text() %>%
  tibble(area = .) %>%
  slice(1:51) %>%
  mutate(area = as.numeric(str_replace(area, ",", "")))
```

Create states data:

```{r create-states}
states_no_abb <- bind_cols(state_names, state_areas)
states <- full_join(state_abb, states_no_abb)
```

## Write data out

```{r write-data}
write_csv(dn, path = "data-for-lab/dennys.csv")
write_csv(lq, path = "data-for-lab/laquinta.csv")
write_csv(states, path = "data-for-lab/states.csv")
```

# In lab

## Data wrangling

### In / out US

Are there any Denny's locations outside the US? Nope!

```{r dn-non-us}
dn %>%
  filter(!(state %in% states$abbreviation))
```

Are there any LA Quinta locations outside the US? YUP! -> *Ask students to figure out where they are.*

```{r lq-non-us}
lq %>%
  filter(!(state %in% states$abbreviation))
```

Mark country for La Quinta -> *Give some as started, rest they should have to figure out*

```{r lq-add-country}
lq <- lq %>%
  mutate(country = case_when(
    state %in% state.abb     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Columbia",
    state == "FM"            ~ "Honduras",
    TRUE                     ~ "Mexico"
  ))
```

Mark country for Denny's

```{r dn-add-country}
dn <- dn %>%
  mutate(country = "United States")
```

### Add establishment variable

Do this before `bind_rows` to put everything together

```{r add-establishment}
dn <- dn %>% mutate(establishment = "Denny's") 
lq <- lq %>% mutate(establishment = "La Quinta") 
```

## Counting

How many Denny's per state or per square mile or thousand square miles? *LATTER LOOKS BETTER, ALSO MORE MEANINGFUL*   

```{r count-per-state}
dn %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation")) %>%
  mutate(
    per_sq_mi = n / area,
    per_sq_mi_th = n / (area / 1000)
    )
```

Can do the same for La Quinta as well...

## Visualizing

First need to combine the data:

```{r bind-dn-lq}
dn_lq <- bind_rows(dn, lq)
```

Let's do only US for this:

```{r us-only}
dn_lq_us <- dn_lq %>%
  filter(country == "United States")
```


Write out data at this stage for the shiny app:

```{r}
write_csv(dn_lq_us, path = "data-shiny/dn_lq_us.csv")
```

Then we plot:

```{r viz-standard-col}
ggplot(dn_lq_us, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point(alpha = 0.8)
```

Should we use La Quinta and Denny's colors? BUT THEY UGLY!!!

```{r viz-custom-col}
lq_col <- "#004827"
dn_col <- "#FFDE23"

ggplot(dn_lq_us, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = c(dn_col, lq_col))
```
