---
title: "Deploying TensorFlow Models"
output: html_notebook
---

# Install Tensorflow and Keras

```{r eval=FALSE}
# Install the Tensorflow, Keras and required packages
install.packages("tensorflow")
install.packages("keras")
install.packages("devtools")
install.packages("rsconnect")

# Install TensorFlow locally
tensorflow::install_tensorflow(version = "1.4")
```

# Train MNIST Digit Recognizer

```{r}
library(keras)

# load data
c(c(x_train, y_train), c(x_test, y_test)) %<-% dataset_mnist()

# reshape and rescale
x_train <- array_reshape(x_train, dim = c(nrow(x_train), 784)) / 255
x_test <- array_reshape(x_test, dim = c(nrow(x_test), 784)) / 255

# one-hot encode response
y_train <- to_categorical(y_train, 10)
y_test <- to_categorical(y_test, 10)

# define and compile model
model <- keras_model_sequential()
model %>%
  layer_dense(units = 32, activation = 'relu', input_shape = c(784),
              name = "image") %>%
  layer_dense(units = 16, activation = 'relu') %>%
  layer_dense(units = 10, activation = 'softmax',
              name = "prediction") %>%
  compile(
    loss = 'categorical_crossentropy',
    optimizer = optimizer_rmsprop(),
    metrics = c('accuracy')
  )

# train model
history <- model %>% fit(
  x_train, y_train,
  epochs = 30, batch_size = 128,
  validation_split = 0.2
)
```

# Export the Model

Export as HDF5 a keras model:

```{r}
save_model_hdf5(model, "keras-mnist.hdf5")
```

and as a SavedModel which is common across TensorFlow, Keras and tfestimators:

```{r}
export_savedmodel(model, "keras-mnist")
```

# Test the Model

First, install tfdeploy:

```{r}
devtools::install_github("rstudio/tfdeploy")
```

Then serve locally:

```{r}
library(tfdeploy)
serve_savedmodel("keras-mnist")
```

# Deploy to RStudio Connect

Deploy model to demo server http://conference.rstudioconnect.com/:

```{r}
library(rsconnect)
deployTFModel("keras-mnist")
```

# Use Deployed model from Bash

```{bash}
curl -sd @examples/digit-zero.json http://conference.rstudioconnect.com/content/2/predict
```

# Use model from JavaScript

First, install `kerasjs` from GitHub:

```{r}
devtools::install_github("rstudio/kerasjs")
```

Then, save, convert and preview to JavaScript:

```{r}
library(kerasjs)
kerasjs_convert("keras-mnist.hdf5")
```
