---
output: 
  html_document:
    css: pomological.css
---

```{r setup,echo=FALSE}
library(magrittr)

fruitName <- "pear"
varietyName <- "bartlett"
startYear <- 1886
endYear <- 1942

json <- jsonlite::fromJSON("watercolors.json")
watercolors <- as.data.frame(json)
# janitorial services
watercolors$year <- as.integer(watercolors$year)
watercolors <- watercolors[!is.na(watercolors$year),]

nameFilter <- grep(fruitName, watercolors$common_name, ignore.case = TRUE)
fruit <- watercolors[nameFilter,]

varietyFilter <- grep(varietyName, fruit$variety, ignore.case = TRUE)
variety <- fruit[varietyFilter,]

inDateRange <- variety[variety$year >= startYear & variety$year <= endYear,]
if (nrow(inDateRange) == 0) {
  stop("No fruit matched input parameters.")
}
chosen <- inDateRange[sample(nrow(inDateRange),1),]

# extract counts of the number of measurements in the group that have the
# same property as the chosen
makeCounts <- function(group, chosen) {
  list(
    common_name = sum(group$common_name == chosen$common_name),
    variety = sum(group$variety == chosen$variety),
    geographic_origin = sum(group$geographic_origin == chosen$geographic_origin),
    artist = sum(group$artist == chosen$artist)
  )
}

# fruitNarrowed and varietyNarrowed are true if the user filters
# narrowed the set of watercolors before we made our selection.
fruitNarrowed <- !identical(watercolors, fruit)
varietyNarrowed <- !identical(fruit, variety)

# sameFruit and sameVariety are the watercolors matching our chosen item.
sameFruit <- watercolors[watercolors$common_name == chosen$common_name,]
sameVariety <- sameFruit[sameFruit$variety == chosen$variety,]

# Count records that match our chosen item
watercolorCounts <- makeCounts(watercolors, chosen)
fruitCounts <- makeCounts(sameFruit, chosen)
varietyCounts <- makeCounts(sameVariety, chosen)

allFreq <- plyr::count(na.omit(as.integer(watercolors$year)))
names(allFreq) <- c("year", "collection")

hasNotes <- chosen$notes_on_original != ""

googleSearch <- sprintf("https://www.google.com/search?q=%s",
                        URLencode(paste0(chosen$common_name, " ",
                                         chosen$variety)))
```

## `r chosen$title`

<div style="float:right; margin-left: 40px;">

```{r out.width="400px", echo=FALSE}
source("pomological.R")
thumbnail_url <- find_pomological_thumbnail_url(chosen$id)
knitr::include_graphics(thumbnail_url)
```
</div>

(<a href="`r chosen$wikimedia_url`" target="_blank">Wikimedia</a> | 
<a href="`r chosen$url`" target="_blank">USDA</a> | 
<a href="`r googleSearch`" target="_blank">Google</a>)

**Scientific name:** `r chosen$scientific_name`  
**Common name:** `r chosen$common_name`  
**Variety:** `r chosen$variety`  

The U.S. Department of Agriculture (USDA) Pomological Watercolor Collection 
contains `r nrow(watercolors)` watercolors, lithographs, and line drawings.

There are `r watercolorCounts$common_name` works of `r chosen$common_name` and 
`r watercolorCounts$variety` `r chosen$variety` `r chosen$common_name`.

**Artist:** `r chosen$artist`  

```{r echo=FALSE}
# same artist lets us summarize information about the artist.
sameArtist <- watercolors[watercolors$artist == chosen$artist,]
artist.location <- unique(sameArtist$geographic_origin)
artist.fruit <- unique(sameArtist$common_name)
artist.variety <- unique(sameArtist$variety)
```

This artist was responsible for `r watercolorCounts$artist` entries in the
collection; `r fruitCounts$artist` of those were `r chosen$common_name` and
`r varietyCounts$artist` were `r chosen$variety` `r chosen$common_name`.

Works by the artist were from `r length(artist.location)` different locations,
covering `r length(artist.variety)` different varieties of
`r length(artist.fruit)` fruits.

```{r echo = FALSE, results = 'asis', eval = FALSE}
# Woah. Some artists roam quite a lot. 
cat("Locations by this artist.\n")
cat(paste("*", artist.location), sep = "\n")
```

```{r echo = FALSE, fig.width=4, fig.height=2}
artistFreq <- plyr::count(na.omit(as.integer(sameArtist$year)))
names(artistFreq) <- c("year", "artist")
mfreq <- merge(allFreq, artistFreq, all = TRUE)
mfreq[is.na(mfreq)] <- 0
# make sure we show at least a 10y span
window <- c(max(min(artistFreq$year) - 5, min(mfreq$year)),
            min(max(artistFreq$year) + 5, max(mfreq$year)))
dygraphs::dygraph(mfreq, main = "works by this artist") %>% 
  dygraphs::dyAxis("y", axisLabelWidth = 30) %>%
  #dygraphs::dySeries("artist", label = chosen$artist) %>%
  dygraphs::dyOptions(drawPoints = TRUE, pointSize = 2) %>%
  # dygraphs::dyHighlight(highlightCircleSize = 5, 
  #                       highlightSeriesBackgroundAlpha = 0.2,
  #                       hideOnMouseOut = FALSE, 
  #                       highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dygraphs::dyLegend(width = 300) %>%
  dygraphs::dyRangeSelector(dateWindow = window)
```

**Date created:** `r chosen$date_created`  

```{r echo=FALSE}
sameYear <- watercolors[watercolors$year == chosen$year,]
year.artist <- unique(sameYear$artist)
year.location <- unique(sameYear$geographic_origin)
year.fruit <- unique(sameYear$common_name)
year.variety <- unique(sameYear$variety)
```

The Pomological Watercolor Collection contains `r nrow(sameYear)` works from 
the year `r chosen$year`. These entries covered 
`r length(year.variety)` varieties of `r length(year.fruit)` fruits
produced by `r length(year.artist)` artists in `r length(year.location)`
different locations.

```{r echo = FALSE, fig.width=4, fig.height=2}
fruitFreq <- plyr::count(na.omit(as.integer(sameFruit$year)))
varietyFreq <- plyr::count(na.omit(as.integer(sameVariety$year)))
names(fruitFreq) <- c("year", "fruit")
names(varietyFreq) <- c("year", "variety")
mfreq <- merge(merge(allFreq, fruitFreq, all = TRUE), varietyFreq, all = TRUE)
mfreq[is.na(mfreq)] <- 0
# make sure we show at least a 10y span
window <- c(max(min(varietyFreq$year) - 5, min(mfreq$year)),
            min(max(varietyFreq$year) + 5, max(mfreq$year)))
dygraphs::dygraph(mfreq, main = "works with matching fruit/variety") %>% 
  dygraphs::dyAxis("y", axisLabelWidth = 30) %>%
  #dygraphs::dySeries("fruit", label = chosen$common_name) %>%
  #dygraphs::dySeries("variety", label = chosen$variety) %>%
  dygraphs::dyOptions(drawPoints = TRUE, pointSize = 2) %>%
  dygraphs::dyLegend(width = 300) %>%
  dygraphs::dyRangeSelector(dateWindow = window)
```

**Geographic origin:** `r chosen$geographic_origin`  

```{r echo=FALSE}
sameLocation <- watercolors[watercolors$geographic_origin == chosen$geographic_origin,]
location.artist <- unique(sameLocation$artist)
location.fruit <- unique(sameLocation$common_name)
location.variety <- unique(sameLocation$variety)
```

This location includes works from `r length(location.artist)` artists,
covering `r length(location.variety)` different varieties of
`r length(location.fruit)` fruits.

```{r echo = FALSE, results = 'asis', eval = hasNotes}
cat("**Notes on original:**", chosen$notes_on_original, "\n")
```

<div style="clear:both;"></div>

> <small>`r chosen$rights`</small>
